We have followed the guide in the IT Document.
The guide was explained in details, even though, we had troubles in testing the system into a unique machine because of RAM limitation.
Probably it would have been better to have an instance of the server and of the database running online.


\subsection{Dependency installation}
We firstly installed the backend. To accomply this, on a Windows machine, you should first install ERLang and then install the RabbitMQ server.

After this, we proceed to install MySQL server and configure it following the guide linked in the IT Document.

The RabbitMQ server and MySQL server started automatically after the installation.

It is not clearly specified in the IDT but is also necessary to install a compatible version of Java and Maven (to run the tests). We installed, respectively, version \texttt{1.8.0\_191} and version \texttt{3.6.0}.

\subsection{Backend installation}
We simply extracted the precompiled version of the backend in an empty folder.
From there we launched each microservice executable, starting from \texttt{service-registry} and then all the other jar executables. 

Each service was launched using the command \texttt{java -jar *servicename*.jar}, except the \texttt{api-gateway} which needs an additional command line parameter.
We think that this aspect was not stressed enough in the ITD; in fact in the first place we were not able to start the server correctly because we forgot the above mentioned configuration string.

\subsection{Frontend installation}
We installed the main Android app from the provided apk package in a new Android Emulator instance.
We then started the app, configured the IP of the server clicking on the app logo in the main screen.

To test the Bluetooth connection we installed the main app and the Bluetooth client in two different real devices.

The minimum Android version, as specified in the requirements, was 7.0 which made quite difficult to test since some of us had the version 6.0.
Moreover the app cannot be fully tested through the emulator since it exploit the Bluetooth connection, which cannot be emulated.
However, all the previous remarks were correctly explained in the ITD Document.




