\subsubsection{Reliability}
The system is provided to be reliable in 99\% of the cases. Downtime is prevented since expected and unexpected maintenance proceeding and upgrades do not interfere with the normal activity of the service.
High use of redundancy and process resilience is expected to be used by the components of the system in order to guarantee a low enough failure rate.

\subsubsection{Availability}
In order to guarantee a high reliability, the system is expected to offer an ideal 24/7 service. A 3-nine availability service is expected (8.76 hours/year downtime)

\subsubsection{Security}
All requests of clients of the service must be encrypted using a public-private key mechanism.
User credentials are stored in DBMS, their password is secure and encrypted using hash functions.
Data of user health parameters are stored in DSMS located in cluster computing data platforms, in order to be efficiently processed, stored and queried by companies.
The payment security for the company subscription plan is guaranteed by third-party services. 
\subsubsection{Maintainability}
Maintenance is expected not to interfere with normal use of the applications. In order to guarantee that, all the components of the system are modular, decoupled between each other, and hierarchically organized.
\subsubsection{Portability}
Mobile application is developed to be only used in smartphones, eventually tablets, in order to satisfy requirements of the services.
Smartwatch app also is developed to be used only in smartwatch and similar wearable devices.
Web services used by companies and run organizers could be developed as mobile app in order to increase portability, but it will reduce usability of the software. 
